A Digital Library for Crowds on the Real-Time Social Web

### 2011-05-05 docs/csce_675/paper.tex
added more about the modules

An architecture for our solution is shown in Figure 1.  Data flows from a
crawler, through zero or more filters, to a grouper, and then through zero or
more filters, and then it is finally stored in a MongoDB database.  The various
modules of this architecture are as follows:

@@

\medskip \noindent \textbf{Localcrawl}: This crawler collects data from users
in a region using the standard Twitter API. We started with a tiny sample set
of seed users. It uses snowball sampling to collect more users that are likely
to live in an area. Once we have a list of users

@@

\medskip \noindent \textbf{GeoStream}: This crawler listens to Twitter's
streaming API to find geo-located tweets.  It recieves every geo-located tweet
posted from anywhere in the world.  In the future, this data may be used to
show crowds on a map.

@@

\medskip \noindent \textbf{Mentions}:
For this project, we exclusivly discover crowds based on communtion.

...

The grouper module analyses the data
collected, to determine crowds and adds them to the DBMS. This is the central
module that detects crowds of different types - communication, content,
geo-graphical, etc. In this project we will be discovering crowds based on
communication only. The algorithm to discover crowds is described in
Section~\ref{sec:crowd_algorithm}.

\subsection{Filter}
Filters are used to remove unnecessary data and 
\medskip \noindent \textbf{Filter}: This module is used to filter un-necessary
data from the framework. It can appear both before and after the grouper module
depending upon its funcationality. In the figure we have showed the module
appear before grouper only. When the module appears before the grouper, it is
used to weed out information unnecessary for the grouper. For example in case
of crowd detection, it remove information like spam messages. When the module
appears after the grouper, it cleans the data generated by the grouper. For,
example in case of crowd detection, it analyzes crowds discovered by the
grouper and removes un-necessary crowds, or crowds that don't meet specific
quality guarentees. The module can also have additional functions that support
features like search.

\medskip \noindent \textbf{HTTP JSON RESTful APIs}: This module provides client an interface to the digital library. The module exposes JSON APIs that the clients can use to browze and search the crowds archive.

>>>>

An architecture for our solution is shown in Figure 1.  Data flows from a
crawler, through zero or more filters, to a grouper, and then through zero or
more filters, and then it is finally stored in a MongoDB database.  We went
with an extremely modular architecture to make the system flexible.  We can
easily integrate new crawlers, filters, and groupers into the system.The
various modules of this architecture are described in the remainder of this
section.

@@

\subsubsection{Localcrawl}
This crawler collects data from users
in a region using the standard Twitter API. We started with a tiny sample set
of seed users. It uses snowball sampling to collect more users that are likely
to live in an area. Once we have a list of users

@@

\subsubsection{GeoStream}
This crawler listens to Twitter's
streaming API to find geo-located tweets.  It recieves every geo-located tweet
posted from anywhere in the world.  In the future, this data may be used to
show crowds on a map.

@@

\subsubsection{Mentions}
For this project, we exclusivly discover crowds based on communication.  The
mentions grouper looks for sets of people who are communicating with each
other.  The algorithm to discover crowds is described in
Section~\ref{sec:crowd_algorithm}.

\subsection{Filter}
Filters are used to remove unnecessary data, such as spam tweets, and add
automatically generated metadata to tweets, users, and crowds.  A filter can
appear before or after the grouper module as needed.  In the following
sections, we discuss two filters that we implemented and several that we plan
to add in the future.

\subsubsection{Lucene Filter}
The Lucene module creates a Lucene index from the text of the tweets in a
crowd.  This index is used to speed up searching through the text of the
tweets. This filter is designed so that a crowd can be updated as new data
arrives from a crowd.

\subsubsection{Network Filter}
We also have a network filter that builds a graph that represents the
communication between the users in a crowd. At the moment, it analyzes two things:
degree centrality and clustering coefficient.  The degree centrality is used to
find the most important users in a given crowd. The clustering coefficient of
the crowd is added to the crowd as automatically generated metadata

\subsubsection{Planned Filters}
There are several filters that we have not implemented, but may implement in
the future. The ability to easily add new filters and create an automated
workflow is an important part of our design.
\begin{itemize}
\item Remove users that appear to be spammers.
\item Add metadata to each user that contains an estimate of the users
    location, and some information about the quality of the estimate.
\item Find the key terms in a crowd and add that metadata to the crowd.
\item Summarize the tweets from a crowd.
\end{itemize}

\subsection{HTTP JSON RESTful APIs}: This module provides client an interface to the digital library. The module exposes JSON APIs that the clients can use to browse and search the crowds archive.
